Prediction of the 2020 Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
fixing response type in the model

final_model <- readRDS(here::here("outputs/model","final_model.rds"))
coefs <- readRDS(here::here("outputs/model","coefficients.rds"))
knitr::kable(c, caption = " Table 1: Model Coefficients") %>% kableExtra::kable_styling(latex_options = "scale_down")

@@

cell_counts$estimate <- predict(final_model, newdata = cell_counts)

# post-stratified estimates - number of trump votes
estimate_votes <- cell_counts %>% mutate(predict_prop = proportion * estimate) %>% group_by(state_name) %>% summarise(pred_vote = sum(predict_prop))
estimate_votes

>>>>

final_model <- readRDS(here::here("outputs/model","final_model.rds"))
coefs <- readRDS(here::here("outputs/model","coefficients.rds"))
knitr::kable(coefs, caption = " Table 1: Model Coefficients") %>% kableExtra::kable_styling(latex_options = "scale_down")

@@

cell_counts$estimate <- predict(final_model, newdata = cell_counts, type = "response")

# post-stratified estimates - number of trump votes
estimate_votes <- cell_counts %>% 
  mutate(predict_prop = proportion * estimate) %>% 
  group_by(total_num,state_name) %>% 
  summarise(predicted_vote = sum(predict_prop)) %>% 
  mutate(state_prediction = total_num*predicted_vote)

estimate_votes

cell_counts %>% arrange(num_records)
